Heuristics and Really Hard Instances \\ for Subgraph Isomorphism Problems

### 2016-07-04 talk/talk.tex
Animate
More talking
More talk

\makeatletter
\newenvironment{nearlyplainframe}[2][]{
    \def\beamer@entrycode{\vspace*{-\headheight}}
    \setbeamertemplate{headline}
    {%
        \begin{beamercolorbox}[colsep=1.5pt]{upper separation line head}
        \end{beamercolorbox}
        \begin{beamercolorbox}[ht=0.5ex,dp=0.125ex,%
            leftskip=.3cm,rightskip=.3cm plus1fil]{title in head/foot}%
        \end{beamercolorbox}%
        \begin{beamercolorbox}[ht=0.5ex,dp=0.125ex,%
            leftskip=.3cm,rightskip=.3cm plus1fil]{author in head/foot}%
        \end{beamercolorbox}%
        \begin{beamercolorbox}[colsep=1.5pt]{lower separation line head}
        \end{beamercolorbox}
        \vspace*{\headheight}
    }

@@

    \input{gen-graph-phase}

@@

\begin{nearlyplainframe}[t]{In Two Dimensions?}

@@

    \begin{itemize}
        \item Is this behaviour solver-independent?
        \item Estimating the phase transition location
        \item Using this to rediscover variable and value ordering heuristics
    \end{itemize}

@@

\begin{nearlyplainframe}[t]{What About Induced?}

\begin{nearlyplainframe}[t]{What Changes Between 10 and 20?}

\begin{nearlyplainframe}[t]{Is The Central Region Really Hard?}

\begin{nearlyplainframe}[t]{Constrainedness}

@@

    \begin{itemize}
        \item Is this behaviour solver-independent?
            \begin{itemize}
                \item Also SAT, PB, MIP encodings, reduction to clique.
            \end{itemize}
        \item Estimating the phase transition location
        \item Using this to invent new variable and value ordering heuristics
            \begin{itemize}
                \item But something unexpected happens this time!
            \end{itemize}
    \end{itemize}

>>>>

\makeatletter
\newenvironment{nearlyplainframe}[2][]{
    \def\beamer@entrycode{\vspace*{-\headheight}\vspace*{3pt}}
    \setbeamertemplate{headline}
    {%
        \begin{beamercolorbox}[colsep=1.5pt]{upper separation line head}
        \end{beamercolorbox}
        \begin{beamercolorbox}[ht=0.5ex,dp=0.125ex,%
            leftskip=.3cm,rightskip=.3cm plus1fil]{title in head/foot}%
        \end{beamercolorbox}%
        \begin{beamercolorbox}[ht=0.5ex,dp=0.125ex,%
            leftskip=.3cm,rightskip=.3cm plus1fil]{author in head/foot}%
        \end{beamercolorbox}%
        \begin{beamercolorbox}[colsep=1.5pt]{lower separation line head}
        \end{beamercolorbox}
        \vspace*{\headheight}
    }

@@

    \only<1> {
        \input{gen-graph-phase}
    }
    \only<2> {
        \input{gen-graph-phase-2}
    }

@@

\begin{nearlyplainframe}[t]{In Two Dimensions?}
    \only<1> {
        \input{gen-graph-non-induced-2d}
    }
\end{nearlyplainframe}

@@

    \begin{itemize}
        \item Is this behaviour solver-independent?
        \item Estimating the phase transition location.
        \item Using this to rediscover variable and value ordering heuristics.
    \end{itemize}

@@

\begin{nearlyplainframe}[t]{Induced in 2D}
    \only<1> {
        \input{gen-graph-induced-2d}
    }
\end{nearlyplainframe}

\begin{nearlyplainframe}[t]{What Changes Between 10 and 20?}
    \only<1> {
        \input{gen-graph-induced-2d-2}
    }
\end{nearlyplainframe}

\begin{nearlyplainframe}[t]{Is The Central Region Really Hard?}
    \only<1> {
        \input{gen-graph-induced-2d-middle}
    }
\end{nearlyplainframe}

\begin{nearlyplainframe}[t]{What About Encodings or Reductions?}
    \only<1> {
        \input{gen-graph-induced-2d-alt}
    }
\end{nearlyplainframe}

\begin{nearlyplainframe}[t]{Constrainedness}
    \only<1> {
        \input{gen-graph-induced-2d-kappa}
    }
\end{nearlyplainframe}

@@

    \begin{itemize}
        \item More on solver-independence and reductions.
        \item Estimating the phase transition location.
        \item Using this to invent new variable and value ordering heuristics.
            \begin{itemize}
                \item But something unexpected happens this time!
            \end{itemize}
    \end{itemize}
